To be FAIR: Theory Specification Needs an Update

### 2025-02-21 manuscript.Rmd
closes #30

If we take cumulative knowledge acquisition to be a goal of scientific research, then Reusability is the ultimate purpose of making theory FAIR.
Applied to FAIR theory, reusability requires that  each theory and its associated metadata are richly described with a plurality of accurate and relevant attributes (R1) with a clear and Accessible license for reuse (R1.1).
It should further have detailed provenance (R1.2), 
which is achieved through version control with Git and archival on Zenodo.
Finally, the (meta)data which meets domain-relevant community standards (R1.3).
The Datacite metadata schema offers an initial template in this regard,
and this paper takes one step towards establishing more fine-grained community standards for FAIR theory.
[This is an example of FAIR metadata](https://raw.githubusercontent.com/cjvanlissa/fair_theory/refs/heads/main/DGPSabstract.md) extracted from Zenodo.

>>>>

If we take cumulative knowledge acquisition to be a goal of scientific research, then Reusability is the ultimate purpose of making theory FAIR.
Applied to FAIR theory, reusability requires that  each theory and its associated metadata are richly described with a plurality of accurate and relevant attributes (R1) with a clear and Accessible license for reuse (R1.1).
It should further have detailed provenance (R1.2), 
which is achieved through version control with Git and archival on Zenodo.
Finally, the (meta)data which meets domain-relevant community standards (R1.3).
The Datacite metadata schema offers an initial template in this regard,
and this paper takes one step towards establishing more fine-grained community standards for FAIR theory.
[This is an example of FAIR metadata](https://raw.githubusercontent.com/cjvanlissa/fair_theory/refs/heads/main/example_metadata.json) extracted from Zenodo.
